Real-space computation of $E$/$B$-mode maps I: Formalism, Compact Kernels, and Polarized Filaments

### 2018-06-29 articles/formalism/sections/generalizedeb.tex
updated greens kernel definition, reordered fig 7, cleaned up revisits, cleaned up discussions about telescoping behaviour

An arbirtrary $G(\beta)$ for which $g_{\ell} \neq 1$ can be equivalently thought in terms of the standard $E/B$ fields being convolved with some effective circularly symmetric beam whose radial profile is given by the expression,
%
\beq
b(\beta) = \sum_{\ell=0}^{\ell_{\rm max}} \frac{2 \ell+1}{4 \pi} g_{\ell} P_{\ell}^{0} (\cos{\beta})\,,
\eeq
%
where $g_{\ell}$ is the same harmonic function as that appearing in \eq{eq:generalized_radial_kernel}.
In contrast to the radial function $G(\beta)$ an instrumental beam function appropriately normalized has the property $b(\beta) \rightarrow 1$ as $\beta \rightarrow 0$. Though the real space functions $G(\beta)$ (operating on Stokes parameters) and $b(\beta)$ (operating on scalar $E/B$) are different, in harmonic space they play identical roles.
%
\begin{figure}[!t] 
\centering
\subfigure[\label{fig:bl_gbeta}]{\includegraphics[width=0.48\columnwidth]{Gbeta_for_different_gl_lmax1536.pdf}}
\subfigure[\label{fig:glbl}]{\includegraphics[width=0.48\columnwidth]{gl_for_different_gbeta_lmax1536.pdf}}
\subfigure[\label{fig:gl_bbeta}]{\includegraphics[width=0.48\columnwidth]{Bbeta_for_gl_lmax1536.pdf}}
\caption{\textit{Top left:} The green line depicts the default radial kernel $f(\beta)$ defined in \eq{eq:qu2eb_gen_kernel}, multiplied by an apodized step function $\theta(3 \beta_0)$. The blue and orange lines depict the modified radial function resulting the beam harmonics $b_{\ell}$ corresponding to Gaussian beams with fwhm=15 \& 12 arc-minutes respectively. The red curve depicts an example modified radial function: $G(\beta)=\mathcal{A} \beta^{n_o} \exp{\left[ -\left( \frac{\beta-\beta_s}{\sqrt{2} \sigma} \right)^{n_1} \right]}$ with parameters set to the following values $[n_0=1;\, \beta_s=0 ;\, \sigma = 0.004 ;\, n_1=1.5]$. The black dashed curve depicts the band limited reconstruction of the modified radial function. \textit{Top right:} This figure depicts the harmonic representation of the respective radial functions as indicated by the legend. The dashed curves of the corresponding color depict the inverse of the harmonic functions. \textit{Bottom:} This figure depicts the normalized beam function $b(\beta)$ evaluated from interpreting the respective harmonic functions as those corresponding to an effective instrument beam.}
\label{fig:example_gbeta}
\end{figure}
%

\comment{It is weird the order that the subplots are referenced.}

% Therefore it is possible to interpret the beam harmonic coefficients as those representing some modified radial kernel.
In \fig{fig:example_gbeta}, we examine in more detail the relationship between the modified radial kernels and these beam harmonic coefficients.  
 \fig{fig:gl_bbeta} depicts the radial profile of the  effective beams corresponding to different radial kernels: the standard kernel with a radial cutoff, kernels corresponding to Gaussian smoothings of the $E/B$ fields, an radial function without oscillations and an exponential cutoff.  Note that the smoothing tend to increase the non-locality, indicated by the shifting right of the maxima of the respective kernels, as one may have expected.  The exponential cutoff (red curve) by construction has a very small non-locality (parameterized by $\beta_0$).

>>>>

An arbirtrary $G(\beta)$ for which $g_{\ell} \neq 1$ can be equivalently thought in terms of the standard $E/B$ fields being convolved with some effective circularly symmetric beam whose radial profile is given by the expression,
%
\beq
b(\beta) = \sum_{\ell=0}^{\ell_{\rm max}} \frac{2 \ell+1}{4 \pi} g_{\ell} P_{\ell}^{0} (\cos{\beta})\,,
\eeq
%
where $g_{\ell}$ is the same harmonic function as that appearing in \eq{eq:generalized_radial_kernel}.
In contrast to the radial function $G(\beta)$ an instrumental beam function appropriately normalized has the property $b(\beta) \rightarrow 1$ as $\beta \rightarrow 0$. Though the real space functions $G(\beta)$ (operating on Stokes parameters) and $b(\beta)$ (operating on scalar $E/B$) are different, in harmonic space they play identical roles.
%
\begin{figure}[!t] 
\centering
\subfigure[\label{fig:gl_gbeta}]{\includegraphics[width=0.48\columnwidth]{Gbeta_for_different_gl_lmax1536.pdf}}
\subfigure[\label{fig:glbl}]{\includegraphics[width=0.48\columnwidth]{gl_for_different_gbeta_lmax1536.pdf}}
\subfigure[\label{fig:gl_bbeta}]{\includegraphics[width=0.48\columnwidth]{Bbeta_for_gl_lmax1536.pdf}}
\caption{\textit{Top left:} The green line depicts the default radial kernel $f(\beta)$ defined in \eq{eq:qu2eb_gen_kernel}, multiplied by an apodized step function $\theta(3 \beta_0)$. The blue and orange lines depict the modified radial function resulting the beam harmonics $b_{\ell}$ corresponding to Gaussian beams with fwhm=15 \& 12 arc-minutes respectively. The red curve depicts an example modified radial function: $G(\beta)=\mathcal{A} \beta^{n_o} \exp{\left[ -\left( \frac{\beta-\beta_s}{\sqrt{2} \sigma} \right)^{n_1} \right]}$ with parameters set to the following values $[n_0=1;\, \beta_s=0 ;\, \sigma = 0.004 ;\, n_1=1.5]$. The black dashed curve depicts the band limited reconstruction of the modified radial function. \textit{Top right:} This figure depicts the normalized beam function $b(\beta)$ evaluated from interpreting the respective harmonic functions as those corresponding to an effective instrument beam.  \textit{Bottom:} This figure depicts the harmonic representation of the respective radial functions as indicated by the legend. The dashed curves of the corresponding color depict the inverse of the harmonic functions.}
\label{fig:example_gbeta}
\end{figure}
%

% Therefore it is possible to interpret the beam harmonic coefficients as those representing some modified radial kernel.
In \fig{fig:example_gbeta}, we examine in more detail the relationship between the modified radial kernels and these beam harmonic coefficients.  
 \fig{fig:gl_gbeta} depicts the radial profile of the  effective beams corresponding to different radial kernels: the standard kernel with a radial cutoff, kernels corresponding to Gaussian smoothings of the $E/B$ fields, an radial function without oscillations and an exponential cutoff.  Note that the smoothing tend to increase the non-locality, indicated by the shifting right of the maxima of the respective kernels, as one may have expected.  The exponential cutoff (red curve) by construction has a very small non-locality (parameterized by $\beta_0$).

### 2018-06-29 articles/formalism/sections/kernel_discussion.tex
updated greens kernel definition, reordered fig 7, cleaned up revisits, cleaned up discussions about telescoping behaviour

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\subsection{Quantifying the non-locality of E \& B modes} \label{sec:radial_locality}
\subsection{The non-locality of the real space operators} \label{sec:radial_locality}
%
\begin{figure}[t]
\centering
\includegraphics[width=0.8\columnwidth]{beta_kernel.pdf}
\caption{The figure depicts the radial part of the convolution kernels. These radial function have been evaluated with the band limit fixed at $\ell \in [2,24]$. The vertical dashed line marks the approximate Healpix pixel size of a NSIDE=8, which is the lowest resolution that allows access to $\ell_{\rm max}=24$.}
\label{fig:beta_kernel}
\end{figure}
%
Above, we have explored in detail the  azimuthal dependence of the real space kernels.  Here we probe the radial dependence, which both  determines the non-locality of the operators and encodes all their multipole dependencies. For illustration, \fig{fig:beta_kernel} shows the radial kernels ${_{\mm}f}, {_{\md}f},{_{\mi}f}$, evaluated using the respective multipole sums given in \eq{eq:rad_ker_queb} and \eq{eq:f2_rad_ker} in the band limit $\ell \in [2,24]$. \revisit{We choose a low band limit to evaluate these radial kernels to highlight some key features of their radial profile.}
%
\begin{figure}[t]
%\subfigure{\includegraphics[width=0.96\columnwidth]{rad_ker_fn_of_ellmax.pdf}}
%\subfigure{\includegraphics[width=0.48\columnwidth]{rad_ker_i_fn_of_ellmax.pdf}}
%\subfigure{\includegraphics[width=0.48\columnwidth]{rad_ker_d_fn_of_ellmax.pdf}}
\includegraphics[width=0.325\columnwidth]{rad_ker_fn_of_ellmax.pdf}\hfill
\includegraphics[width=0.325\columnwidth]{rad_ker_i_fn_of_ellmax.pdf}\hfill
\includegraphics[width=0.325\columnwidth]{rad_ker_d_fn_of_ellmax.pdf}
\caption{This figures depicts the radial functions for the different kernels and varying band limit set by fixed $\ell_{\rm min}=2$ and varying $\ell_{\rm max}$ as indicated by their legends. The left panel depicts ${_{\mm}f}(\beta,\ell_{\rm min},\ell_{\rm max})$, the middle panels depicts ${}_{\mi}f(\beta,\ell_{\rm min},\ell_{\rm max})$ and the right panel depicts ${}_{\md}f(\beta,\ell_{\rm min},\ell_{\rm max})$ respectively. All the curves are normalized such that their maxima is set to unity. The horizontal solid black line marks the location where the amplitude of the respective kernels fall below 1\% of its maximum. The thin slanted dashed gray lines indicate a power law fit (by eye) to the envelope of the radial functions. The thick black short vertical dashed lines indicate the transition points as predicted by the empirically derived relation for the non-locality parameter $\beta_0={\rm min}(180^\circ,180^\circ \times 22/\ell_{\rm max})$.}
%While the envelopes for function ${_{\mm}f}(\beta)~\&~ {}_{\mi}f(\beta)$ are fit well by the power law $\propto \beta^{-1.5}$, the envelope for the function ${}_{\md}f(\beta)$ is seen to have a slightly steeper slope $\propto \beta^{-1.65}$.}
\label{fig:rad_ker_decay}
\end{figure}
%

The function ${_{\mm}f}$ is the radial part of the kernel that translates the Stokes parameters $Q$/$U$ to scalars $E$/$B$ and vice versa.  It oscillates and, as a consequence of the spin-2 symmetry, it vanishes as $\beta \rightarrow 0$ and $\beta \rightarrow \pi$, since the Euler angles $\alpha$, $\gamma$ are not uniquely defined at those separations.
%This nature of ${_{\mm}f}$ is critical to ensure that the derived fields have the necessary spin properties.

The radial part of the kernel that decomposes the  Stokes parameters into parts that correspond to $E$ and $B$ modes  are also  necessarily non-local.  The function \revisit{${_{\mi}f}$ is the radial part of the band limited delta function $\mi$.  It expectedly has its maxima at $\beta=0$ and decays with increasing angular separation.  ${_{\md}f}$ has a vanishing value in the region where $\beta \rightarrow 0$ however it does not vanish at $\beta \rightarrow \pi$ as seen in \fig{fig:beta_kernel}.}

@@

The resultant set of radial function are depicted in \fig{fig:rad_ker_decay}. While the amplitude of these radial function scales up as $\propto \ell_{\rm max}^2$, for clarity in the plot their global maxima are normalized to unity.  This normalization highlights the key feature, that on increasing $\ell_{\rm max}$ the radial kernels shift left, attaining their global maxima at progressively small angular distances $\beta$.  At intermediate values of $\beta$, the envelope of the radial functions is fit well by a power law $ \propto \beta^{-n}$ as seen in \fig{fig:rad_ker_decay}.
In fact these finding are neatly summarized in the observation that the radial functions computed by evaluating the multipole sums to different maximum multipoles are approximately self-similar and follow this telescoping and scaling property: $${}_rf(\beta,2,\ell_{\rm max}) \approx \Big[\frac{\ell_{\rm max}}{\ell'_{\rm max}}\Big]^2{}_rf(\beta'=\frac{\ell'_{\rm max}}{\ell_{\rm max}} \beta ,2,\ell'_{\rm max}) \,,$$ where ${}_rf$ denotes all the different radial functions.

\revisit{We can now understand the shifting left of the radial kernels on increasing the maximum multipole using this telescoping property. Lets say the function ${}_rf(\beta', \ell'_{\rm max})$ transition to being monotonously below some fraction of the global maxima at an angular distance of $\beta'_0$.  The function ${}_rf(\beta, \ell_{\rm max})$, given $\ell_{\rm max} > \ell'_{\rm max}$, reaches the same transition point at a smaller angular distance $\beta$. The amplitude scaling of the functions is irrelevant since the transition point is always described in terms of the fraction of the global maxima of the function.}  \revisit{[K: there is not a lot of content to this paragraph...  It just says higher lmax falls below a fixed threshold faster, but this is already in the plot and surrounding paragraphs.]}

To quantify the non-locality of the scalar modes $E/B$, we can define a characteristic angular radius of the region from which the kernels get most of their contribution.   We define a non-locality parameter $\beta_{0}$ as the angle beyond which the function ${_{\mm}f}(\beta,\ell_{\rm min}=2,\ell_{\rm max})$ consistently falls below 1\% of its maximum.
%For $\ell_{\rm max}=24$, the maximum multipole accessible on a Nside=8 Healpix map, the non-locality parameter $\beta_0=180^{\circ}$ as the radial function never falls monotonously below 1\% of its global maxima as seen in \fig{}. Using this fact and the self similar property of the radial functions, we define the following empirical relation: $\beta_o= {\rm min}(180,180 \frac{24}{\ell_{\rm max}})$, as a means of estimating the non-locality parameter given the maximum multipole $\ell_{\rm max}$ accessible for analysis.
\revisit{The empirical relation:
\beq
\beta_0= {\rm min}\left(180^\circ,180^\circ \frac{\ell_{0}}{\ell_{\rm max}} \right) \,,
\eeq
with $\ell_{0}=22$ provides a reasonable estimate of this transition point for ${}_{\mm}f$ as seen in \fig{fig:rad_ker_decay}. Setting $\ell_{0}=10$ and $\ell_{0}=32$ predicts the transition points for the functions ${}_{\mi}f$ and  ${}_{\md}f$ respectively.} \comment{How sensitive is this transition point to $\ell{\rm min}$?} \comment{K: What do we get in a rolling window of size $\beta_0/5$ or something to average over a few oscillations?}

\comment{Compare the fitted slope to the one in the Zaldariaga paper.}
\revisit{In the flat sky limit it has been argued that form of the radial function has to be ${}_\mm f(\beta)\simeq\beta^{-2}$ so as to ensures that the Fourier modes for Stokes parameters $Q/U$ are related  to the $E/B$ Fourier modes merely by rotations and with no scale dependent factor \cite{Zaldarriaga2001a}. In this work we formally derive the function form of ${}_\mm f(\beta)$, which is seen to have an oscillatory nature and find that that the envelope of the function scales as $\beta^{-1.55}$.}
\comment{So whats the point and is this discussion better suited for the conclusions? Could the fit by eye be highly misleading? }

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\subsection{Quantifying the non-locality of E \& B modes} \label{sec:radial_locality}
\subsection{The non-locality of the real space operators} \label{sec:radial_locality}
%
\begin{figure}[t]
\centering
\includegraphics[width=0.8\columnwidth]{beta_kernel.pdf}
\caption{The figure depicts the radial part of the convolution kernels. These radial function have been evaluated with the band limit fixed at $\ell \in [2,24]$. The vertical dashed line marks the approximate Healpix pixel size of a NSIDE=8, which is the lowest resolution that allows access to $\ell_{\rm max}=24$.}
\label{fig:beta_kernel}
\end{figure}
%
Above, we have explored in detail the  azimuthal dependence of the real space kernels.  Here we probe the radial dependence, which both  determines the non-locality of the operators and encodes all their multipole dependencies. For illustration, \fig{fig:beta_kernel} shows the radial kernels ${_{\mm}f}, {_{\md}f},{_{\mi}f}$, evaluated using the respective multipole sums given in \eq{eq:rad_ker_queb} and \eq{eq:f2_rad_ker} in the band limit $\ell \in [2,24]$. We choose a low band limit to evaluate these radial kernels to highlight some key features of their radial profile.
%
\begin{figure}[t]
%\subfigure{\includegraphics[width=0.96\columnwidth]{rad_ker_fn_of_ellmax.pdf}}
%\subfigure{\includegraphics[width=0.48\columnwidth]{rad_ker_i_fn_of_ellmax.pdf}}
%\subfigure{\includegraphics[width=0.48\columnwidth]{rad_ker_d_fn_of_ellmax.pdf}}
\includegraphics[width=0.325\columnwidth]{rad_ker_fn_of_ellmax.pdf}\hfill
\includegraphics[width=0.325\columnwidth]{rad_ker_i_fn_of_ellmax.pdf}\hfill
\includegraphics[width=0.325\columnwidth]{rad_ker_d_fn_of_ellmax.pdf}
\caption{This figures depicts the radial functions for the different kernels and varying band limit set by fixed $\ell_{\rm min}=2$ and varying $\ell_{\rm max}$ as indicated by their legends. The left panel depicts ${_{\mm}f}(\beta,\ell_{\rm min},\ell_{\rm max})$, the middle panels depicts ${}_{\mi}f(\beta,\ell_{\rm min},\ell_{\rm max})$ and the right panel depicts ${}_{\md}f(\beta,\ell_{\rm min},\ell_{\rm max})$ respectively. All the curves are normalized such that their maxima is set to unity. The horizontal solid black line marks the location where the amplitude of the respective kernels fall below 1\% of its maximum. The thin slanted dashed gray lines indicate a power law fit (by eye) to the envelope of the radial functions. The thick black short vertical dashed lines indicate the transition points as predicted by the empirically derived relation for the non-locality parameter $\beta_0={\rm min}(180^\circ,180^\circ \times 22/\ell_{\rm max})$.}
%While the envelopes for function ${_{\mm}f}(\beta)~\&~ {}_{\mi}f(\beta)$ are fit well by the power law $\propto \beta^{-1.5}$, the envelope for the function ${}_{\md}f(\beta)$ is seen to have a slightly steeper slope $\propto \beta^{-1.65}$.}
\label{fig:rad_ker_decay}
\end{figure}
%

The function ${_{\mm}f}$ is the radial part of the kernel that translates the Stokes parameters $Q$/$U$ to scalars $E$/$B$ and vice versa.  It oscillates and as a consequence of the spin-2 symmetry, it vanishes as $\beta \rightarrow 0$ and $\beta \rightarrow \pi$, since the Euler angles $\alpha$, $\gamma$ are not uniquely defined at those separations.
%This nature of ${_{\mm}f}$ is critical to ensure that the derived fields have the necessary spin properties.

The radial part of the kernel that decomposes the  Stokes parameters into parts that correspond to $E$ and $B$ modes  are also  necessarily non-local.  The function ${_{\mi}f}$ is the radial part of the band limited delta function $\mi$.  It expectedly has its maxima at $\beta=0$ and decays with increasing angular separation.  ${_{\md}f}$ has a vanishing value in the region where $\beta \rightarrow 0$ however it does not vanish at $\beta \rightarrow \pi$ as seen in \fig{fig:beta_kernel}.

@@

The resultant set of radial function are depicted in \fig{fig:rad_ker_decay}. While the amplitude of these radial function scales up as $\propto \ell_{\rm max}^2$, for clarity in the plot their global maxima are normalized to unity.  This normalization highlights the key feature, that on increasing $\ell_{\rm max}$ the radial kernels shift left, attaining their global maxima at progressively small angular distances $\beta$.  At intermediate values of $\beta$, the envelope of the radial functions is fit well by a power law $ \propto \beta^{-n}$ as seen in \fig{fig:rad_ker_decay}.
In fact these finding are neatly summarized in the observation that the radial functions computed by evaluating the multipole sums to different maximum multipoles are approximately self-similar and follow this telescoping and scaling property: $${}_rf(\beta,2,\ell_{\rm max}) \approx \Big[\frac{\ell_{\rm max}}{\ell'_{\rm max}}\Big]^2{}_rf(\beta'=\frac{\ell'_{\rm max}}{\ell_{\rm max}} \beta ,2,\ell'_{\rm max}) \,,$$ where ${}_rf , r \in [\mm, \md,\mi]$ denotes all the different radial functions. \revisit{We can now understand the amplitude scaling and the shifting left of the radial kernels on increasing the maximum multipole by studying this telescoping property. Specifically the global maxima of the kernel with maximum multipole $\ell_{max}$ is amplified/supressed by a factor $(\ell_{\rm max}/\ell'_{\rm max})^2$ and the oscillating part is compressed/expanded by a factor $(\ell'_{\rm max}/\ell_{\rm max})^{-1}$ with respect to the kernel defined by the maximum multipole $\ell'_{\rm max}$.}

To quantify the non-locality of the scalar modes $E/B$, we can define a characteristic angular radius of the region from which the kernels get most of their contribution.   We define a non-locality parameter $\beta_{0}$ as the angular distance beyond which the function ${_{\mm}f}(\beta,\ell_{\rm min}=2,\ell_{\rm max})$ transitions to being consistently below 1\% of its maximum.
%For $\ell_{\rm max}=24$, the maximum multipole accessible on a Nside=8 Healpix map, the non-locality parameter $\beta_0=180^{\circ}$ as the radial function never falls monotonously below 1\% of its global maxima as seen in \fig{}. Using this fact and the self similar property of the radial functions, we define the following empirical relation: $\beta_o= {\rm min}(180,180 \frac{24}{\ell_{\rm max}})$, as a means of estimating the non-locality parameter given the maximum multipole $\ell_{\rm max}$ accessible for analysis.
The empirical relation:
\beq
\beta_0= {\rm min}\left(180^\circ,180^\circ \frac{\ell_{0}}{\ell_{\rm max}} \right) \,,
\eeq
with $\ell_{0}=22$ provides a reasonable estimate of this transition point for ${}_{\mm}f$ as seen in \fig{fig:rad_ker_decay}. Setting $\ell_{0}=10$ and $\ell_{0}=32$ predicts the transition points for the functions ${}_{\mi}f$ and  ${}_{\md}f$ respectively.%\comment{How sensitive is this transition point to $\ell{\rm min}$?}

In the flat sky limit it has been argued that form of the radial function has to be ${}_\mm f(\beta)\simeq\beta^{-2}$ so as to ensures that the Fourier modes for Stokes parameters $Q/U$ are related  to those of $E/B$ modes merely by rotations and with no scale dependent factor \cite{Zaldarriaga2001a}. Here we numerically studied the formally derived radially function ${}_\mm f(\beta)$ which reveals an oscillatory nature whose amplitude decays on increasing angular distance. We find that the the positive envelope of the function scales as $\beta^{-1.55}$.
\comment{K: What do we get in a rolling window of size $\beta_0/5$ or something to average over a few oscillations?}

### 2018-06-29 articles/formalism/sections/kernel_paintbrush.tex
updated greens kernel definition, reordered fig 7, cleaned up revisits, cleaned up discussions about telescoping behaviour

%\revisit{A stacking analysis of Planck data \citep{2016A&A...586A.141P} sees $E>0$ along filaments (selected from intensity data), but no $B$-mode signal is above the noise.  We predict that it should be there in higher fidelity data.}
A stacking analysis of Planck data \citep{2016A&A...586A.141P} sees $E>0$ along filaments (selected from intensity data), but claim no $B$-mode signal above the noise. We predict that a B-mode signal from filaments should be present, since they have a finite length of a few degrees.  Detecting B-modes from filaments will be easier with more signal-to-noise and may require a more careful filament analysis, rescaling and aligning the filament ends.  The detectability of the $B$-mode signature from stacked filaments in Planck data calls for a more careful assessment, we should see it in higher-fidelity data.

>>>>

%\revisit{A stacking analysis of Planck data \citep{2016A&A...586A.141P} sees $E>0$ along filaments (selected from intensity data), but no $B$-mode signal is above the noise.  We predict that it should be there in higher fidelity data.}
A stacking analysis of Planck data \citep{2016A&A...586A.141P} sees $E>0$ along filaments (selected from intensity data), but claim no $B$-mode signal above the noise. We predict that a B-mode signal from filaments should be present, since they have a finite length of a few degrees.  Detecting B-modes from filaments will be easier with more signal-to-noise and may require a more careful filament analysis, rescaling and aligning the filament ends.  While the detectability of the $B$-mode signature from stacked filaments in Planck data calls for a more careful assessment, we should see it in higher-fidelity data.
